---
title: "UDISC"
author: "ME :)"
date: "2023-02-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

## importing the stats (Change per run)

code to import all of the stats into a df

```{r}
udisc_path <- "E:\\Obsidian vault\\Personal Notes\\R\\Projects\\UDISC\\Stats\\Dad2-23-2023.csv"

udisc_stats <- read.csv(udisc_path)

#creating primary key
udisc_stats <- mutate(udisc_stats,
                      Course_ID = paste(udisc_stats$CourseName, ": ", udisc_stats$LayoutName, ": "))
```

## Just solo stats (Change per run)

Getting The specific persons name, and using that to filter data down to just their rounds

```{r}

Just_One_Name <- "Ben"
Just_One_Name

Just_One <- filter(udisc_stats, PlayerName == Just_One_Name)
Just_One
```

## Average strokes on the nth hole

for now, over entire career

```{r}
First_hole_Avg <- mean(Just_One$Hole1)
First_hole_Avg

Second_hole_Avg <- mean(Just_One$Hole2)
Second_hole_Avg

Third_hole_Avg <- mean(Just_One$Hole3)
Third_hole_Avg

Fourth_hole_Avg <- mean(Just_One$Hole4)
Fourth_hole_Avg

Fifth_hole_Avg <- mean(Just_One$Hole5)
Fifth_hole_Avg

Sixth_hole_Avg <- mean(Just_One$Hole6)
Sixth_hole_Avg

Seventh_hole_Avg <- mean(Just_One$Hole7)
Seventh_hole_Avg

Eighth_hole_Avg <- mean(Just_One$Hole8)
Eighth_hole_Avg

Ninth_hole_Avg <- mean(Just_One$Hole9)
Ninth_hole_Avg

Front_Nine_Avgs <- c(First_hole_Avg, Second_hole_Avg, Third_hole_Avg, Fourth_hole_Avg, Fifth_hole_Avg, Sixth_hole_Avg, Seventh_hole_Avg, Eighth_hole_Avg, Ninth_hole_Avg)
Front_Nine_Avgs
```

## calculate par averages

```{r}
#create table the combines all courses into one row, and counts number of times played
Playcounts <- group_by(Just_One, Course_ID,) %>% 
   summarize(
    n()
  )

Playcounts <- Playcounts %>% distinct(.keep_all = TRUE)

#Just courses played by the main person
Just_One_Course <- c(Playcounts$Course_ID)

#Total number of games played
Total_Games <- as.numeric(nrow(Just_One))

#getting the par for each course played
Pars <- filter(udisc_stats, PlayerName == "Par" ) 

Pars <- Pars %>% select(-Date)

Pars <- group_by(Pars, Course_ID, Hole1, Hole2, Hole3, Hole4, Hole5, Hole6, Hole7, Hole8, Hole9, Hole10, Hole11, Hole12, Hole13, Hole14, Hole15, Hole16, Hole17, Hole18, Hole19, Hole20, Hole21, Hole22, Hole23, Hole24)

# get rid of dupes
Pars <- Pars[!duplicated(Pars$Course_ID), ]

# THE MAGIC CODE
Pars <- filter(Pars, Course_ID %in% Playcounts$Course_ID)

#ordering pars and Playcounts by Course_ID to get them in the same order

Pars <- Pars[order(Pars$Course_ID), ]

Playcounts <- Playcounts[order(Playcounts$Course_ID), ]


#get weighted average of par for each hole: sum of (par * ((this holes playcount)/(total hole one playcount)))
First_hole_Avg_Par <- sum(Pars$Hole1*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Second_hole_Avg_Par <- sum(Pars$Hole2*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Third_hole_Avg_Par <- sum(Pars$Hole3*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Fourth_hole_Avg_Par <- sum(Pars$Hole4*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Fifth_hole_Avg_Par <- sum(Pars$Hole5*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Sixth_hole_Avg_Par <- sum(Pars$Hole6*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Seventh_hole_Avg_Par <- sum(Pars$Hole7*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Eighth_hole_Avg_Par <- sum(Pars$Hole8*(Playcounts$`n()` / sum(Playcounts$`n()`)))

Ninth_hole_Avg_Par <- sum(Pars$Hole9*(Playcounts$`n()` / sum(Playcounts$`n()`)))

#assign values to vector
Front_Nine_Avg_Pars <- c(First_hole_Avg_Par, Second_hole_Avg_Par, Third_hole_Avg_Par, Fourth_hole_Avg_Par, Fifth_hole_Avg_Par, Sixth_hole_Avg_Par, Seventh_hole_Avg_Par, Eighth_hole_Avg_Par, Ninth_hole_Avg_Par)
Front_Nine_Avg_Pars

```

## Calculate avg score on the nth hole

```{r}
Rel_Score <- (Front_Nine_Avgs - Front_Nine_Avg_Pars)
```

## Plotting Average strokes on each hole (holes 1-9)

```{r}
#get the ylimit to have extra space on the bottom, for labels

Ylim_One <- min(Front_Nine_Avgs-.03)
Ylim_Two <- max(Front_Nine_Avgs)


ggplot(data = df, aes(x = 1:9, y = Front_Nine_Avgs, label = Rel_Score), xlims = c(1,9), ylims = c(Ylim_Rel_One, Ylim_Rel_Two) ) +
  geom_point() + 
  labs(title = paste("Avg strokes on the nth hole for:", Just_One_Name ), x = "Hole #", y = "Avg Strokes (Lower is Better)")+ 
  scale_x_continuous(breaks = seq(1,9 , by = 1)) + 
  scale_y_continuous(breaks = round(seq(Ylim_One, Ylim_Two, .1), digits=2)) +
  geom_text(label = round(Front_Nine_Avgs, digits = 2), hjust = 0,nudge_x = -0.125, nudge_y = -0.03)
```

## Plotting Avg score on the nth hole

```{r}
#Put Rel_Score into a data frame
df <- data.frame(Rel_Score, 1:9)

Ylim_Rel_One <- min(Rel_Score-.03)
Ylim_Rel_Two <- max(Rel_Score)


ggplot(data = df, aes(x = 1:9, y = Rel_Score, label = Rel_Score), xlims = c(1,9), ylims = c(Ylim_Rel_One, Ylim_Rel_Two) ) +
  geom_point() + 
  labs(title = paste("Avg score on the nth hole for:", Just_One_Name ), x = "Hole #", y = "Avg Score (Lower is Better)")+ 
  scale_x_continuous(breaks = seq(1,9 , by = 1)) + 
  scale_y_continuous(breaks = round(seq(Ylim_Rel_One, Ylim_Rel_Two, .1), digits=2)) +
  geom_text(label = round(Rel_Score, digits = 2), hjust = 0,nudge_x = -0.125, nudge_y = -0.03)
```
